Fixing Vulnerabilities Hinders Maintainability

### 2019-02-07 paper/ICPC19/icpc19.tex
histogram size adjustment
table descriptive stats projects with zero decimals

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.4\textwidth]{figures/language_dist.pdf}
 	\caption{Distribution of Security Refactorings per Language\Luis{esta figure pode ser maior nao pode?}}
	\label{fig:lang}
\end{figure}

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.4\textwidth]{figures/type_dist.pdf}
 	\caption{Distribution of the Domain of Projects}
	\label{fig:domain}
\end{figure}

@@

\begin{table*}[h]
	\centering
	\caption{Descriptive statistics of the dataset projects}
\begin{tabular}{@{}rrrrrrrrrrr@{}}
\toprule
      & Forks   & Stars   & Watchers & Contributors & Commits  & Branches & Releases & Size      & Issues & Pull Requests  \\ \midrule
mean  & 1763.52 & 5448.74 & 401.37   & 153.33       & 14834.17 & 45.17    & 129.45   & 122973.24 & 3768.97   & 1941.61 \\
std   & 2434.03 & 6215.09 & 486.60   & 123.68       & 22234.46 & 150.15   & 189.93   & 209732.51 & 5933.16   & 3603.31 \\
min   & 1.00       & 3.00       & 1.00        & 0.00            & 103.00      & 1.00        & 0.00        & 108.00       & 0.00         & 0.00       \\
25\%  & 391.50  & 1581.00    & 117.25   & 49.00           & 1440.50  & 4.00        & 19.00       & 8466.75   & 313.75    & 143.25  \\
median  & 838.50  & 2836.50 & 248.00      & 99.00           & 5504.50  & 9.00        & 59.00       & 37372.50  & 1792.50   & 650.00     \\
75\%  & 2155.00    & 6828.50 & 459.50   & 261.00          & 18579.25 & 20.00       & 142.75   & 117699.50 & 4087.75   & 1907.25 \\
max   & 16366.00   & 31841.00   & 3446.00     & 413.00          & 114378.00   & 1227.00     & 1114.00     & 995790.00    & 33970.00     & 19329.00   \\
Total & 165771.00  & 512182.00  & 37729.00    & 14413.00        & 1394412.00  & 4246.00     & 12168.00    & 11559485.00  & 354283.00    & 182511.00  \\ \bottomrule
\end{tabular}
\label{tab:dataset}
\end{table*}

>>>>

\begin{figure}[h]
 	\centering 	\includegraphics[width=\linewidth]{figures/language_dist.pdf}
 	\caption{Distribution of Security Refactorings per Language\Luis{esta figure pode ser maior nao pode?}}
	\label{fig:lang}
\end{figure}

\begin{figure}[h]
 	\centering 	\includegraphics[width=\linewidth]{figures/type_dist.pdf}
 	\caption{Distribution of the Domain of Projects}
	\label{fig:domain}
\end{figure}

@@

\begin{table*}[h]
	\centering
	\caption{Descriptive statistics of the projects in the dataset}
\begin{tabular}{@{}rrrrrrrrrrr@{}}
\toprule
      & Forks   & Stars   & Watchers & Contributors & Commits  & Branches & Releases & Size      & Issues & Pull Requests  \\ \midrule
mean  & 1763 & 5448 & 401   & 153       & 14834 & 45    & 129   & 122973 & 3768   & 1941 \\
std   & 2434 & 6215 & 486   & 123       & 22234 & 150   & 189   & 209732 & 5933   & 3603 \\
min   & 1       & 3       & 1        & 0            & 103      & 1        & 0        & 108       & 0         & 0       \\
25\%  & 391  & 1581    & 117   & 49           & 1440  & 4        & 19       & 8466   & 313    & 143  \\
median  & 838  & 2836 & 248      & 99           & 5504  & 9        & 59       & 37372  & 1792   & 650     \\
75\%  & 2155    & 6828 & 459   & 261          & 18579 & 20       & 142   & 117699 & 4087   & 1907 \\
max   & 16366   & 31841   & 3446     & 413          & 114378   & 1227     & 1114     & 995790    & 33970     & 19329   \\
Total & 165771  & 512182  & 37729    & 14413        & 1394412  & 4246     & 12168    & 11559485  & 354283    & 182511.00  \\ \bottomrule
\end{tabular}
\label{tab:dataset}
\end{table*}
